The Need to Develop a Holistic Infectious Disease Surveillance System

### 2024-10-20 manuscript/manuscript.qmd
Update manuscript plots

>>>>

```{julia}
#| fig-cap: "The difference in the proportion of the time series in alert - proportion in an outbreak,of outbreak detection systems under different testing rates and noise structures. The shaded bands illustrate the 80% central interval, and the solid/dashed lines represent the mean estimate."
#| label: fig-delay
alert_outbreak_proportion_line_plot
```
